My title

### 2024-10-24 paper/paper.qmd
Update model result part.

# Join electoral vote data with Trump's predictions
state_predictions <- merge(total_trump, electoral_votes, by = "state")

@@

# Create a table showing the prediction results
library(knitr)
kable(state_predictions, col.names = c("State", "Trump Predicted %", "Electoral Votes", "Winner"),
      digits = 2, caption = "Prediction for Trump by State")
```

>>>>

# Combine electoral vote data with Trump's predictions
state_predictions <- merge(total_trump, electoral_votes, by = "state")

@@

# Calculate the electoral votes for each candidate
state_predictions$trump_electoral_votes <- ifelse(state_predictions$winner == "Trump", state_predictions$electoral_votes, 0)
state_predictions$harris_electoral_votes <- ifelse(state_predictions$winner == "Harris", state_predictions$electoral_votes, 0)

# Summarize total electoral votes for each candidate
trump_electoral_votes <- sum(state_predictions$trump_electoral_votes)
harris_electoral_votes <- sum(state_predictions$harris_electoral_votes)

# Create a table showing the prediction results
library(knitr)

# Create the table using kable
kable(state_predictions[, c("state", "predicted_percent_trump", "electoral_votes", "winner")], 
      col.names = c("State", "Trump Predicted %", "Electoral Votes", "Winner"), 
      digits = 2, 
      caption = "Prediction for Trump by State")

# Print the results for the total electoral votes
print(paste("Trump Electoral Votes:", trump_electoral_votes))
print(paste("Harris Electoral Votes:", harris_electoral_votes))
```

```{r}
summary(regression_model)
```
